Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2022-03-11 reportTII-ArticleHIL.tex

\begin{IEEEkeywords}
Enter key words or phrases in alphabetical 
order, separated by commas. For a list of suggested keywords, send a blank 
e-mail to keywords@ieee.org or visit \underline
{http://www.ieee.org/organizations/pubs/ani\_prod/keywrd98.txt}
\end{IEEEkeywords}

@@

Once the model was created, it was exported to Simulink and further tested. One test involved using constant blocks to represent the pressure voltages, position voltages, and desired pedal position for a given time instant in the first brake log. The actual pedal position and the error between the desired and actual pedal positions were then plotted. The actual pedal position plot can be seen in \autoref{brakeWorkspacePedalPosition}. The resulting error plot between the desired pedal position and the model generated position can be found in \autoref{brakeWorkspacePedalError}.

\begin{figure}[h]
	\centering
	\subcaptionbox{ \label{brakeWorkspacePedalPosition}}
		{\includegraphics[width=0.48\linewidth]{figs/img/brakeSysActualPedalPositionFromWorkspaceBlocks}}
	\subcaptionbox{ \label{brakeWorkspacePedalError}}
		{\includegraphics[width=0.48\linewidth]{figs/img/brakeSysPedalPositionErrorFromWorkspaceBlocks}}
	\caption{Actual Pedal Position and Error Plots Using the From Workspace Block}
\end{figure}

>>>>

\begin{IEEEkeywords}
Hardware-in-the-Loop, Neural Network, System Identification
\end{IEEEkeywords}

@@

Once the model was created, it was exported to Simulink and tested again. One test involved using To Workspace blocks to access the pressure voltages, position voltages, and desired pedal position values in the first brake log. These values were used as inputs for the model, and the actual pedal position along with the error between the desired and actual pedal positions were then plotted. The actual pedal position plot can be seen in \autoref{brakeWorkspacePedalPosition}. The resulting error plot between the desired pedal position and the model generated position can be found in \autoref{brakeWorkspacePedalError}. Despite an initial spike within the first few seconds of the graph, the error plot shows that the difference between the pedal positions generated by the system and the desired pedal positions is never more than 5\%.

\begin{figure}[h]
	\centering
	\subcaptionbox{Actual Pedal Position \label{brakeWorkspacePedalPosition}}
		{\includegraphics[width=0.48\linewidth]{figs/img/brakeSysActualPedalPositionFromWorkspaceBlocks}}
	\subcaptionbox{Error Between the Actual and Desired Pedal Position \label{brakeWorkspacePedalError}}
		{\includegraphics[width=0.48\linewidth]{figs/img/brakeSysPedalPositionErrorFromWorkspaceBlocks}}
	\caption{Actual Pedal Position and Error Plots Using the From Workspace Blocks}
\end{figure}

The second test used constant blocks to represent the voltages and desired pedal position at a specific time instant in the first brake log. The error and the actual pedal position were then plotted again. The pedal position plot is shown in \autoref{brakeConstantsPedalPosition}, and the error plot is represented by \autoref{brakeConstantsPedalError}. As the plots show, the model is able to produce the desired pedal position and the error falls to 0\% after a spike at the start.

\begin{figure}[h]
	\centering
	\subcaptionbox{Actual Pedal Position \label{brakeConstantsPedalPosition}}
		{\includegraphics[width=0.48\linewidth]{figs/img/brakeSysActualPedalPositionConstantBlocks}}
	\subcaptionbox{Error Between the Actual and Desired Pedal Position \label{brakeConstantsPedalError}}
		{\includegraphics[width=0.48\linewidth]{figs/img/brakeSysPedalPositionErrorConstantBlocks}}
	\caption{Actual Pedal Position and Error Plots Using the Constant Blocks}
\end{figure}
